Graph Generators for Data Science: A Survey

### 2018-06-07 introduction.tex
pass on prior work

To the best of our knowledge, our work is the first surveying the broad landscape of graph data generators spanning different Big Data applications and
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently data-driven and not meant to serve the purpose of letting any
researcher or practitioner interested in Big Data be able to make a guided
choice of the desired
generator based on its functional and goal-driven features (such as the application domain,
the supported operations and the key configuration options).
Moreover, our work is much broader and targets graph generators of several
diversified communities, not limiting its scope to few generators of the database
and graph processing communities.

>>>>

To the best of our knowledge, our work is the first surveying the broad
landscape of graph data generators spanning different data science applications and
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently data-driven and not meant to serve the purpose of letting any
researcher or practitioner interested in data science make a guided
choice of the desired
generator based on its functional and goal-driven features (such as the application domain,
the supported operations and the key configuration options).
Moreover, our work is much broader and targets graph generators of several
diversified communities, not limiting its scope to few generators of the database
and graph processing communities.
